\Large \bf 3-Step, 1-Factor Authentication With Custom-Fit, In-Ear EEG

### 2017-02-06 paper.tex
minor + gitignore
USENIX style

% Created 2017-02-05 Sun 21:39
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{ffff}
\date{\today}
\title{1-Step, 3-Factor Authentication with Custom-Fit, In-Ear EEG}
\hypersetup{
 pdfauthor={ffff},
 pdftitle={1-Step, 3-Factor Authentication with Custom-Fit, In-Ear EEG},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 25.1.1 (Org mode 9.0.4)}, 
 pdflang={English}}
\begin{document}

\maketitle
\begin{abstract}
In this paper, we present a system that provides 3-factors of authentication (knowledge, posession and inherence) in a single step, using brain-based authentication via a custom-fit, in-ear EEG. Across all subjects, we achieve a best-case XX\% false acceptance, XX\% false rejection rate with data from only one earpiece. In a preliminary test of an ``imposter'' spoof attack, we find a 0\% false acceptance rate. \underline{Conclusions and relevance}.
\end{abstract}

@@

Research in in-ear EEG is only several years old. Nonetheless, the concept has
attracted a lot of attention because of the discreetness factor of in-ear EEG over
traditional scalp-based EEG. A research team at the Imperial College London
and Aarhus University published a landmark paper in 2011 that introduced the
concept of in-ear EEG, demonstrating for the first time the feasibility of recording
brainwave signals from within the ear canal. Follow-up work from the same
group demonstrated its ability to produce signal-to-noise ratios comparable to
those from conventional EEG electrode placements, robustness to common
sources of artifacts, and use in a brain-computer interface (BCI) system based on
auditory evoked potentials and visual evoked potentials.
\uline{Citation to our pst work} 
was the first to merge these two streams of work, using in-ear EEG signals for
user authentication with a consumer-grade device. United Sciences is currently
developing a consumer hearable called The Aware that will measure EEG from the ear.
Behavioral authentication methods such as keystroke dynamics and speaker
authentication can be categorized as one-step two-factor authentication
schemes. In both cases, the knowledge factor (password or passphrase) and
inherence factor (typing rhythm or speaker’s voice) are employed. In contrast, the
Nymi band supports one-step two-factor authentication via the inherence
factor (cardiac rhythm that is supposed to be unique to each individual) and the
possession factor (the wearing of the band on the wrist). However, as far as we
know, no one has proposed or demonstrated a one-step three-factor
authentication scheme.
\section{Methods}
\label{sec:org63d105c}
\subsection{{\bfseries\sffamily TODO} Manufacturing, materials}
\label{sec:orgb483219}
\subsection{Subjects}
\label{sec:orgaf30da9}
\subsection{{\bfseries\sffamily TODO} Tasks}
\label{sec:org86eea32}

\uline{Explain stuff around tasks}

@@

\begin{table}[h]
\centering
\begin{tabular}{lllll}
Task & External stimuli? & Personal secret? & Eyes? & Imagery?\\
\hline
Breathe & No & No & Closed & None\\
Breathe - open & No & No & Open & None\\
Sport & No & Yes & Closed & Motor\\
Song & No & Yes & Closed & Aural\\
Song - open & No & Yes & Open & Aural\\
Speech & No & Yes & Closed & Aural\\
Listen - Tone & Yes & No & Closed & None\\
Listen - ASSR & Yes & No & Closed & None\\
Face & No & Yes & Closed & Visual\\
Sequence & Yes & Yes & Open & Visual\\
\hline
\end{tabular}
\caption{Properties of authentication tasks. We selected tasks with a variety of different properteries, but preferred tasks that did not require external stimuli, as the need to present such stimuli at authentication time could present challenges for usability, and user security.}
\end{table}
\subsection{Protocol}
\label{sec:org2041857}
Our initial participants were recruited from a nearby university and scheduled for ear molding
and impedance checking sessions. Finally, the data collection visit was scheduled and took
approximately 90 minutes for set up and experiment execution. The OpenBCI system we used
allows for 8 channels of simultaneous recording, along with separate ground and reference channels.
Data was initially collected with the ground placed at the center of the forehead, and using the left
mastoid as reference, though we can easily re-reference to another channel by subtracting a desired
channel (such as right mastoid). Each earpiece (shown in the image below) contain three channels: 
one placed on the helix, and two inside the canal - one front-facing and the other back-facing. The remaining
two channels were placed on the right mastoid for later re-referencing, and at approximately Fp1 (on the 
forehead above the left eye) for validating the data collected in the ears against a scalp-based measure. 
Before beginning the experiment, the data from all channels was visualized and participants were asked to
blink and clench their jaws to confirm visibly that all channels were active and properly connected.

@@

\uline{Figure: Plot of FAR/FRR by electrode combination, XGBoost and LinearSVC}.

@@

\uline{Our main result:}

\uline{Table: FAR/FRR Between-subjects results by participant (avg. all tasks? Best task?)}

\uline{Our attempt to substantiate that we have both inherence and knowledge factors:}

\uline{Table: original strategy, within-subjects, within-tasks strategy; where each of those headings is subdivided into mean FAR, mean FRR (across all subjects and tasks)}

@@

\uline{Quantitative and qualitative data, where appropriate}

>>>>

% TEMPLATE for Usenix papers, specifically to meet requirements of

% https://www.usenix.org/conference/usenixsecurity17/submitting-papers

% Complaints to /dev/null.
% This version uses the latex2e styles, not the very ancient 2.09 stuff.
\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{lib/usenix,epsfig,endnotes}
\begin{document}

%don't want date printed
\date{}

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf 3-Step, 1-Factor Authentication With Custom-Fit, In-Ear EEG}

%for single author (just remove % characters)
\author{
{\rm Your N.\ Here}\\
Your Institution
\and
{\rm Second Name}\\
Second Institution
% copy the following lines to add more authors
% \and
% {\rm Name}\\
%Name Institution
} % end author

\maketitle

% Use the following at camera-ready time to suppress page numbers.
% Comment it out when you first submit the paper for review.
\thispagestyle{empty}

\subsection*{Abstract}
In this paper, we present a system that provides 3-factors of authentication (knowledge, posession and inherence) in a single step, using brain-based authentication via a custom-fit, in-ear EEG. Across all subjects, we achieve a best-case XX\% false acceptance, XX\% false rejection rate with data from only one earpiece. In a preliminary test of an ``imposter'' spoof attack, we find a 0\% false acceptance rate. \underline{Conclusions and relevance}.

@@

Research in in-ear EEG is only several years old. Nonetheless, the concept has
attracted a lot of attention because of the discreetness factor of in-ear EEG over
traditional scalp-based EEG. A research team at the Imperial College London
and Aarhus University published a landmark paper in 2011 that introduced the
concept of in-ear EEG, demonstrating for the first time the feasibility of recording
brainwave signals from within the ear canal. Follow-up work from the same
group demonstrated its ability to produce signal-to-noise ratios comparable to
those from conventional EEG electrode placements, robustness to common
sources of artifacts, and use in a brain-computer interface (BCI) system based on
auditory evoked potentials and visual evoked potentials.
\underline{Citation to our past work} 
was the first to merge these two streams of work, using in-ear EEG signals for
user authentication with a consumer-grade device. United Sciences is currently
developing a consumer hearable called The Aware that will measure EEG from the ear.
Behavioral authentication methods such as keystroke dynamics and speaker
authentication can be categorized as one-step two-factor authentication
schemes. In both cases, the knowledge factor (password or passphrase) and
inherence factor (typing rhythm or speaker’s voice) are employed. In contrast, the
Nymi band supports one-step two-factor authentication via the inherence
factor (cardiac rhythm that is supposed to be unique to each individual) and the
possession factor (the wearing of the band on the wrist). However, as far as we
know, no one has proposed or demonstrated a one-step three-factor
authentication scheme.
\section{Methods}
\label{sec:org63d105c}
\subsection{{\bfseries\sffamily TODO} Manufacturing, materials}
\label{sec:orgb483219}
\subsection{Subjects}
\label{sec:orgaf30da9}
\subsection{{\bfseries\sffamily TODO} Tasks}
\label{sec:org86eea32}

\underline{Explain stuff around tasks}

@@

\begin{table}[h]
\centering
\begin{tabular}{lllll}
Task & External stimuli? & Knowledge factor ? & Eyes? & Imagery?\\
\hline
Breathe & No & No & Closed & None\\
Breathe - open & No & No & Open & None\\
Sport & No & Yes & Closed & Motor\\
Song & No & Yes & Closed & Aural\\
Song - open & No & Yes & Open & Aural\\
Speech & No & Yes & Closed & Aural\\
Listen - Tone & Yes & No & Closed & None\\
Listen - ASSR & Yes & No & Closed & None\\
Face & No & Yes & Closed & Visual\\
Sequence & Yes & Yes & Open & Visual\\
\hline
\end{tabular}
\caption{Properties of authentication tasks. We selected tasks with a variety of different properteries, but preferred tasks that did not require external stimuli, as the need to present such stimuli at authentication time could present challenges for usability, and user security.}
\end{table}
\subsection{Protocol}
\label{sec:org2041857}
Our initial participants were recruited from a nearby university and scheduled for ear molding
and impedance checking sessions. Finally, the data collection visit was scheduled and took
approximately 90 minutes for set up and experiment execution. The OpenBCI system we used
allows for 8 channels of simultaneous recording, along with separate ground and reference channels.
Data was initially collected with the ground placed at the center of the forehead, and using the left
mastoid as reference, though we can easily re-reference to another channel by subtracting a desired
channel (such as right mastoid). Each earpiece (shown in the image below) contain three channels: 
one placed on the helix, and two inside the canal - one front-facing and the other back-facing. The remaining
two channels were placed on the right mastoid for later re-referencing, and at approximately Fp1 (on the 
forehead above the left eye) for validating the data collected in the ears against a scalp-based measure. 
Before beginning the experiment, the data from all channels was visualized and participants were asked to
blink and clench their jaws to confirm visibly that all channels were active and properly connected.

@@

\underline{Figure: Plot of FAR/FRR by electrode combination, XGBoost and LinearSVC}.

@@

\underline{Our main result:}

\underline{Table: FAR/FRR Between-subjects results by participant (avg. all tasks? Best task?)}

\underline{Our attempt to substantiate that we have both inherence and knowledge factors:}

\underline{Table: original strategy, within-subjects, within-tasks strategy; where each of those headings is subdivided into mean FAR, mean FRR (across all subjects and tasks)}

@@

\underline{Quantitative and qualitative data, where appropriate}
